%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{fontawesome5}
\usepackage[backref]{hyperref} 
\hypersetup
{   pdfauthor = UnnamedOrange,
	colorlinks = true,
	linkcolor = black,
	anchorcolor = black,
	citecolor = black,
	urlcolor = black
}


\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Yanglang Yuan} % Your name
\address{1088 Xueyuan Avenue, Shenzhen 518055, P.R. China} % Your address
\address{ {\href{mailto:11930509@mail.sustech.edu.cn}{\raisebox{-0.2\height}\faEnvelope\  {11930509@mail.sustech.edu.cn}}}
{~~~~~~\href{https://yuanyl.eu.org} {\raisebox{-0.2\height} \faLink\ {yuanyl.eu.org}}}
%{~~\href{https://www.researchgate.net/profile/Yanglang-Yuan}{\raisebox{-0.2\height}\faResearchgate\ {researchgate.net/Yanglang Yuan}}}
~~~~~~
{\faCalendar\ {Updated: May 2023}} }


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

%{\bf Southern University of Science and Technology} \hfill {\em Sept. 2021 - June 2024(Expected)} \\ 
%{M.Sc. in Electronic Science and Technology} \hfill {Shenzhen, China}
{\bf Southern University of Science and Technology} \hfill { Sept. 2021 - June 2024 (Expected)} \\ 
{M.Sc. in Electronic Science and Technology} \hfill {Shenzhen, China}

{\bf Southern University of Science and Technology} \hfill { Sept. 2015 - June 2019} \\ 
{B.Eng. in Mechanical Engineering} \hfill {Shenzhen, China}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications \& patents}

    \begin{rSubsection}{Journal Papers}{}{}{}

        \item Shiquan Ling,{ \textbf{Yanglang Yuan}, Danqi Yan, Yuquan Leng, Yiming Rong, George Q. Huang. (2022). “RHYTHMS: Real-time Data-driven Human-machine Synchronization for Proactive Ergonomic Risks Mitigation in the Context of Industry 4.0 and Beyond", \textit{SSRN Electronic Journal}}.\\
        \href{http://dx.doi.org/10.2139/ssrn.4153658}{{doi: 10.2139/ssrn.4153658.}}

        \item {\textbf{Yanglang Yuan}, Daqiang Guo, Shiquan Ling, Jingke Wang, Guyue Zhou, Yiming Rong, Yongsheng Ma. (2023). “A framework for Customer-to-Manufacturer~(C2M)~in the context of Industry 5.0"} \textit{(Under Review)}

        \vspace{-5pt}    
    \end{rSubsection}

        \begin{rSubsection}{Conference}{}{}{}

        \item {\textbf{Yanglang Yuan}, Jingke Wang, Kangtang, Guyue Zhou, Yiming Rong, Yongsheng Ma. (2023). “A framework and implementation of Customer-to-Manufacturer (C2M) paradigm in e-Commerce"} \textit{(NSFC-RGC Conference 2023, Hong Kong)}

        \vspace{-5pt}    
    \end{rSubsection}

      %  \begin{rSubsection}{Journal Papers}{}{}{}
      %   \item {\textbf{Yanglang Yuan}, J. Grezmak, Yiming Rong, K. Daltorio(2022), “A Review of Individual Customization in Manufacturing System", 
       %  \textit{Soft Robotics, Brif Communication(Published)}} \\
        % \vspace{-10pt}


       %  \item {J1 J. Zhou, Q. Nguyen, S. Kamath, Y. Hacohen, \textbf{C.Zhu}, M. Fu, K. Daltorio(2022), “Hands to Hexapods, Wearable User Interface Design for Specifying Leg Placement for Legged Robots", \textit{Frontiers in Robotics and AI(Submitted)}}
       % \end{rSubsection}
       % \vspace{-8pt}
     % \begin{rSubsection}{Conference Papers}{}{}{}
     %     \item {C1 \textbf{C.Zhu}, F. Han, J. Yi,  “Wearable Sensing and Knee Exoskeleton Control for Awkward Gaits Assistance", \textit{2022 IEEE 18th International Conference on Automation Science and Engineering Mexico City, Mexico(Submitted)}}
     % \end{rSubsection}

       \begin{rSubsection}{Patents}{}{}{}
       \item { \textbf{Yanglang Yuan}, Jiahui Zhang, Xiaoyu Zhang, Fan Zhou, Yajun Wang, Hui Li, Haijiang Wang. Fuel cell bipolar plate and fuel cell: CN, 110459780A[P]. 2019-11-05.}
       \vspace{2pt}
       
       \item { \textbf{Yanglang Yuan}, Jiahui Zhang, Xiaoyu Zhang, Fan Zhou, Yajun Wang, Hui Li, Haijiang Wang. Fuel cell bipolar plate and fuel cell: CN, 210429963U[P]. 2019-07-25.}
       
       
       \end{rSubsection} 
    
            
\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experiences}

    \begin{rSubsection}{Intelligent Manufacturing Lab at SUSTech}{July 2021 - Present}{Advisor: Prof. Yiming (Kevin) Rong, Prof. Yongsheng Ma}{Shenzhen, China}
    \vspace{-4pt}
    \item \textbf{Researching for Customer-to-Manufacturer(C2M) } \\
    Data-driven intelligent manufacturing systems;\\
    C2M manufacturing system model with universality and completeness;\\
    3D printing sneakers based on C2M scene.
    \end{rSubsection}
    
    %------------------------------------------------
    
    \begin{rSubsection}{Shenzhen Key Laboratory of Hydrogen Energy}{June 2017 - June 2019}{Advisor: Prof. Haijiang Wang}{Shenzhen, China}
    \vspace{-4pt}
    \item \textbf{A Bipolar Plate Design for Fuel Cell} \\
    Mechanical structure design of a novel bipolar plate for fuel cell unmanned aerial vehicle (UAV);\\
    Simulated in SolidWorks and COMSOL for the static and dynamic analysis.

    \item \textbf{A Controlling System for Fuel Cell}\\ 
    Designed the control logic and methods \& controller of the fuel cell system; \\
    Designed the temperature and voltage patrol detection system of Fuel Cell.\\
    Thesis topic: Controlling System of the fuel cell in the UAV
%    \item \textbf{Geotechnical Modeling for CRAB-Like Robot Locomotion on Granular Medias}\\
 %   Built hexapod robot model in Webots simulator and developed a tripod gait controller;\\
  %  Designed experiments to derive the leg-terrain interaction model based on Resistive Force Theory;\\
   % Proposed a way to reduce the overlapping time of stance for different gaits and minimize the sinkage.

    \end{rSubsection}

    \begin{rSubsection}{Seoul National University - SUSTech Research Program}{Dec. 2017 - Jan. 2018}{Advisor: Prof. Keyang Tang}{Shenzhen, China}
        \vspace{-4pt}
        \item \textbf{International Winter Undergraduate Research Experience} \\
        Worked in mixed teams with Seoul National University students to complete specific research tasks;\\ 
        Analysis of the development of the intelligent manufacturing industry.
    \end{rSubsection}

    \begin{rSubsection}{Robotics and Autonomy Lab at Tsinghua University}{June 2017 - Aug. 2017}{Advisor: Prof. Chenglong Fu}{Beijing, China}
        \vspace{-4pt}
        \item \textbf{Summer Undergraduate Research Project} \\
        Participated in the design and manufacturing of a robot Bluetooth communication controller; \\
        Other advanced knowledge in Robotics.
    \end{rSubsection}

    \begin{rSubsection}{Formula Student Electric China Program}{2016 - 2017}{Advisor: Prof. Yiming (Kevin) Rong}{Shenzhen, China}
        \vspace{-4pt}
        \item \textbf{The Controlling System of Electric Racing}  \hfill { Jan. 2017 - Aug. 2017}\\
        In charge of the electronic part of the racing car;
        Designed the control logic and methods of electric racing;\\
        Bulit the Battery Management System(BMS) of electric racing.
        % \item \textbf{Battery Management System(BMS) of Electric Racing}  \hfill { June 2016 - Jan. 2017}\\
        % Research on the control strategy of the battery management system; \\
        % Designed and built the temperature and voltage detection circuit of a battery management system.

    \end{rSubsection}
 
\end{rSection}
%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}
   
\begin{rSubsection}{Advanced Manufacturing Systems}{Feb. 2022 - June 2022}{Teaching Assistant}{Shenzhen, China}
\item Responsible for introducing computer-aided design (CAD), computer-aided manufacturing (CAM), process control, quality control, etc.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Awareness Practices of Manufacturing Engineering}{Sept. 2021 - Jan. 2022}{Teaching Assistant}{Shenzhen, China}
\item Responsible for preparation of equipment, data analysis, and presentation of results and conclusions of the students' course projects.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
    \vspace{-5pt}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Certificate & GCDF \\
Programming & Proficient: MATLAB, Plant Simulation;   ~~Intermediate: C/C++, Java \\
Technical Tools & Solidworks, AutoCAD, CNC, Altium Designer, LaTeX, Markdown, etc. \\
%Language & Chinese, Cantonese, English
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	THONORS AND AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}
     \vspace{-8pt}
    \item {Outstanding Postgraduate Student, SUSTech}   \hfill {2022}  
     \vspace{-5pt}
    \item {Excellent Postgraduate Teaching Assistant, SUSTech}   \hfill {2021 - 2022}  
     \vspace{-5pt}
    \item {Employee of the Year, SUSTech}   \hfill {2021}  
     \vspace{-5pt}
    \item {Outstanding Graduation Thesis, SUSTech}        \hfill {2019}
     \vspace{-5pt}
    \item {Honorary Graduate of Zhicheng Residential College, SUSTech}   \hfill {2019}
     \vspace{-5pt}
    \item {Self-improvement Star of Zhicheng Residential College, SUSTech}   \hfill {2019}
     \vspace{-5pt}
    \item {National Encouragement Scholarship, China}        \hfill {2018}
     \vspace{-5pt}
    \item {Outstanding Leadership of Zhicheng Residential College, SUSTech} \hfill {2016 - 2018}
    \vspace{-5pt}  
     \item {Winning Award of Formula Student Electric China} \hfill {2017}
    \vspace{-5pt}
%     \item {Winning Award of Formula Student Electric China} \hfill {2017}
 %   \vspace{-5pt}
%   \item {Outstanding Student Representative of Student Congress, SUSTech} \hfill {2017}

%  \vspace{-5pt}  
%    \item {Outstanding Student Representative of Student Congress, SUSTech}    \hfill {2017}
     


%    \item {First-Class SUSTech Scholarship for Outstanding Students}        \hfill {2018}  Academic progress award
%    \vspace{-5pt}
%    \item {Third-Class SUSTech Scholarship for Outstanding Student}         \hfill {2015-2017}
%    \vspace{-5pt}    
    \end{rSection}


\begin{rSection}{REFEREES}

   \vspace{-8pt}
  \item {Prof. \href{mailto:rongym@sustech.edu.cn}{Yiming Rong}, Southern University of Science and Technology, rongym@sustech.edu.cn} 
    \vspace{-5pt}
  \item {Prof. \href{mailto:mays@sustech.edu.cn}{Yongsheng Ma}, Southern University of Science and Technology, mays@sustech.edu.cn}  
    \vspace{-5pt}
%   \item {Prof. \href{mailto:xusl@sustech.edu.cn}{Shaolin Xu}, Southern University of Science and Technology, xusl@sustech.edu.cn}  
%     \vspace{-5pt}
        
        \end{rSection}



%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
